Nitrogen cycling in the CLM5: controls on responses to environmental forcing

### 2018-11-07 figures.tex

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/rel_GPP.png}
     \caption{GPP CO2 and N respones}
     \label{GPP CO2 and N respones}
  \end{figure}

 \begin{figure}[h]
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/rel_NPP.png}
     \caption{NPP CO2 and N respones}
     \label{NPP CO2 and N respones}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/rel_LAI.png}
     \caption{LAI CO2 and N respones}
     \label{LAI CO2 and N respones}
  \end{figure}

>>>>

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/OCT_CNdep_GPP1_CLM50defpft_ndep_1x1pt_US-Me2_ens_MIC_p2001.png}
     \caption{GPP CO2 and N respones}
     \label{GPP CO2 and N respones 2001}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/OCT_CNdep_GPP1_CLM50defpft_ndep_1x1pt_US-Me2_ens_MIC_p2006.png}
     \caption{GPP CO2 and N respones}
     \label{GPP CO2 and N respones 2006}
  \end{figure}

 \begin{figure}[h]
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/OCT_CNdep_NPP1_CLM50defpft_ndep_1x1pt_US-Me2_ens_MIC_p2006.png}
     \caption{NPP CO2 and N respones}
     \label{NPP CO2 and N respones}
  \end{figure}

 \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/OCT_CNdep_TLAI1_CLM50defpft_ndep_1x1pt_US-Me2_ens_MIC_p2001.png}
     \caption{LAI CO2 and N respones 2001}
     \label{LAI CO2 and N respones}
  \end{figure}

   \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/OCT_CNdep_TLAI1_CLM50defpft_ndep_1x1pt_US-Me2_ens_MIC_p2006.png}
     \caption{LAI CO2 and N respones 2006}
     \label{LAI CO2 and N respones}
  \end{figure}

\begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/OCT_CNdep_LEAFN1_CLM50defpft_ndep_1x1pt_US-Me2_ens_MIC_p2006.png}
     \caption{Leaf Nitrogen  CO2 and N respones}
     \label{Leaf Nitrogen CO2 and N respones}
  \end{figure}
